---
title: "Tips and Tricks"
description: |
  Notes on how to use Sykdomspulsen Analytics infrastructure
date: 2021-06-02
author:
  - first_name: "Chi"
    last_name: "Zhang"
    url: https://www.fhi.no
    affiliation: Folkehelseinstituttet
    affiliation_url: https://www.fhi.no
output:
  distill::distill_article:
    toc: true
    toc_depth: 2
editor_options: 
  chunk_output_type: console
---


```{r setup, include=FALSE}
unloadNamespace("scexample")
unloadNamespace("sc")
knitr::opts_chunk$set(collapse = TRUE)
options(knitr.kable.NA = '')
library(data.table)
library(scexample)
library(magrittr)
```

## FAQ


## Data, argset, schema

It is necessary to know which **analysis** you are working on. All the analyses within a task can be accessed by `sc::tm_get_plans_argsets_as_dt()`. 

```{r, echo=T}
options(width = 150)
# if don't know which plan to choose, can examine by 
#sc::tm_get_plans_argsets_as_dt('ui_autoc19_report_county')
```

## Running tasks

### Run externally (without manually loading data into environment)

The analysis (**main function**) is run in loops, with data/argset/schema iterating over all combinations. 

The following two are equivalent: 

```{r, echo=T, eval=F}
tm_run_task('analysis_covid_metrics')
```

What it actually does: 

```{r, echo=T, eval=F}
retval <- list()

# 1:5 is an example
for(index_plan in 1:5){  
  # data is the same for each plan
  data <- plans[[index_plan]]$get_data()
  
  # argset could be different for the SAME DATA
  for(index_analysis in 1:5){
    argset <- plans[[index_plan]]$get_argset(index_analysis)
    
    # then run the MAIN ANALYSIS 
    retval[[index]] <- analysis_covid_metrics(data = data, argset = argset) # schema = schema
  }
}
```

### Run internally (manually)

Since we do not run with the loop above, it is necessary to specify **ONE set of data/argset/schema** manually. This is done with the following. 

```{r, echo=T, eval=F}
if(plnr::is_run_directly()){
  # sc::tm_get_plans_argsets_as_dt("skuhr_import_data_recent")

  index_plan <- 7
  index_analysis <- 1

  data <- sc::tm_get_data("skuhr_import_data_recent", index_plan = index_plan)
  argset <- sc::tm_get_argset("skuhr_import_data_recent", index_plan = index_plan, index_analysis = index_analysis)
  schema <- sc::tm_get_schema("skuhr_import_data_recent")
}
```

As this chunk is INSIDE the main function, it overwrites the argument values. 

## Changelog {.appendix}

2021-06-02: Originally published.
