---
title: "File Layout"
description: |
  Which files go where, and what is in them?
date: 2021-07-14
author:
  - first_name: "Richard Aubrey"
    last_name: "White"
    url: https://www.fhi.no
    affiliation: Folkehelseinstituttet
    affiliation_url: https://www.fhi.no
    orcid_id: 0000-0002-6747-1726
output:
  distill::distill_article:
    toc: true
    toc_depth: 2
    toc_float: true
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(collapse = TRUE)
options(knitr.kable.NA = '')
library(sykdomspulsen)
library(data.table)
library(magrittr)
library(sc)
```

## Introduction

Implementing Sykdomspulsen Core requires a number of functions to be called in the correct order. To make this as simple as possible, we have provided a skeleton implementation at https://github.com/folkehelseinstituttet/scskeleton

We suggest that you clone this GitHub repo to your server, and then do a global find/replace on `scskeleton` with the name you want for your R package.

Descriptions of the required files/functions are detailed below.

## 00_env_and_namespace.r

https://github.com/folkehelseinstituttet/scskeleton/blob/main/R/00_env_and_namespace.r

```{r, echo=FALSE, results='asis'}
options(width = 150)
x <- fhiplot::as_github_code("https://raw.githubusercontent.com/folkehelseinstituttet/scskeleton/main/R/00_env_and_namespace.r")
print(x, include_url_as_link = TRUE)
```

## 01_definitions.r

https://github.com/folkehelseinstituttet/scskeleton/blob/main/R/01_definitions.r

```{r, echo=FALSE}
options(width = 150)
x <- fhiplot::as_github_code("https://raw.githubusercontent.com/folkehelseinstituttet/scskeleton/main/R/01_definitions.r")
print(x, include_url_as_link = TRUE)
```

## 02_permissions.r

https://github.com/folkehelseinstituttet/scskeleton/blob/main/R/02_permissions.r

```{r, echo=FALSE}
options(width = 150)
x <- fhiplot::as_github_code("https://raw.githubusercontent.com/folkehelseinstituttet/scskeleton/main/R/02_permissions.r")
print(x, include_url_as_link = TRUE)
```

## 03_db_schemas.r

https://github.com/folkehelseinstituttet/scskeleton/blob/main/R/03_db_schemas.r

```{r, echo=FALSE}
options(width = 150)
x <- fhiplot::as_github_code("https://raw.githubusercontent.com/folkehelseinstituttet/scskeleton/main/R/03_db_schemas.r")
print(x, include_url_as_link = TRUE)
```

## 04_tasks.r

https://github.com/folkehelseinstituttet/scskeleton/blob/main/R/04_tasks.r

```{r, echo=FALSE}
options(width = 150)
x <- fhiplot::as_github_code("https://raw.githubusercontent.com/folkehelseinstituttet/scskeleton/main/R/04_tasks.r")
print(x, include_url_as_link = TRUE)
```

## 05_deliverables.r

https://github.com/folkehelseinstituttet/scskeleton/blob/main/R/05_deliverables.r

```{r, echo=FALSE}
options(width = 150)
x <- fhiplot::as_github_code("https://raw.githubusercontent.com/folkehelseinstituttet/scskeleton/main/R/05_deliverables.r")
print(x, include_url_as_link = TRUE)
```

## 06_config.r

https://github.com/folkehelseinstituttet/scskeleton/blob/main/R/06_config.r

```{r, echo=FALSE}
options(width = 150)
x <- fhiplot::as_github_code("https://raw.githubusercontent.com/folkehelseinstituttet/scskeleton/main/R/06_config.r")
print(x, include_url_as_link = TRUE)
```

## 07_onLoad.r

https://github.com/folkehelseinstituttet/scskeleton/blob/main/R/07_onLoad.r

```{r, echo=FALSE}
options(width = 150)
x <- fhiplot::as_github_code("https://raw.githubusercontent.com/folkehelseinstituttet/scskeleton/main/R/07_onLoad.r")
print(x, include_url_as_link = TRUE)
```

## 08_onAttach.r

https://github.com/folkehelseinstituttet/scskeleton/blob/main/R/08_onAttach.r

```{r, echo=FALSE}
options(width = 150)
x <- fhiplot::as_github_code("https://raw.githubusercontent.com/folkehelseinstituttet/scskeleton/main/R/08_onAttach.r")
print(x, include_url_as_link = TRUE)
```

## 99_util_*.r

https://github.com/folkehelseinstituttet/scskeleton/blob/main/R/99_util_no_data_plot.r

```{r, echo=FALSE}
options(width = 150)
x <- fhiplot::as_github_code("https://github.com/folkehelseinstituttet/scskeleton/blob/main/R/99_util_no_data_plot.r")
print(x, include_url_as_link = TRUE)
```


## Task files

Task files are placed in .r files under their own names.

### weather_download_and_import_rawdata.r

https://github.com/folkehelseinstituttet/scskeleton/blob/main/R/weather_download_and_import_rawdata.r

```{r, echo=FALSE}
options(width = 150)
x <- fhiplot::as_github_code("https://raw.githubusercontent.com/folkehelseinstituttet/scskeleton/main/R/weather_download_and_import_rawdata.r")
print(x, include_url_as_link = TRUE)
```

### weather_clean_data.r

https://github.com/folkehelseinstituttet/scskeleton/blob/main/R/weather_clean_data.r

```{r, echo=FALSE}
options(width = 150)
x <- fhiplot::as_github_code("https://raw.githubusercontent.com/folkehelseinstituttet/scskeleton/main/R/weather_clean_data.r")
print(x, include_url_as_link = TRUE)
```

### weather_export_weather_plots.r

https://github.com/folkehelseinstituttet/scskeleton/blob/main/R/weather_export_plots.r

```{r, echo=FALSE}
options(width = 150)
x <- fhiplot::as_github_code("https://raw.githubusercontent.com/folkehelseinstituttet/scskeleton/main/R/weather_export_plots.r")
print(x, include_url_as_link = TRUE)
```

## Changelog {.appendix}

2021-07-14: Draft created.

